Semantic Linearity in a Lazy Optimising Compiler

### 2025-07-11 popl26.tex
made popl26 file

To determine whether the usage of a binding from a recursive group is
linear,
we must infer the superset of resources that may end up being consumed
in a single use of any of the bindings. For a strongly connected recursive
group, this superset is the same for all bindings by definition.
%
Intuitively, this inference amounts to finding a set of linear resources
($\Delta$) that satisfies the set of equations derived from the bindings
$\ov{x_i}$ in the group such that
%\begin{enumerate}
occurrences of $x_i$ in its own body are synonymous with using all resources in $\Delta$ exactly once.
%(2) and if the binding $x$ is fully evaluated, then all resources in $\Delta$ are consumed exactly once.
%\end{enumerate}
%Finding a solution to this equation is akin to finding a (principle) type for a
%recursive binding such that occurrences of itself in its definition are also well-typed.
%
It follows from the solution being the same for all bindings that
at most a single variable from the recursive group can be used in the continuation.
%
The treatment of recursive let bindings in our system is discussed in Section~\ref{sec:recursivelets}.

>>>>

To determine whether the usage of a binding from a recursive group is linear,
we must infer the superset of resources that may end up being consumed in a
single use of any of the bindings. For a strongly connected recursive group,
this superset is the same for all bindings by definition.
%
% Intuitively, this inference amounts to finding the linear resources
% ($\Delta$) which satisfy set of equations derived from the bindings
% $\ov{x_i}$ in the group such that
% %\begin{enumerate}
% occurrences of $x_i$ in its own body are synonymous with using all resources in $\Delta$ exactly once.
%(2) and if the binding $x$ is fully evaluated, then all resources in $\Delta$ are consumed exactly once.
%\end{enumerate}
%Finding a solution to this equation is akin to finding a (principle) type for a
%recursive binding such that occurrences of itself in its definition are also well-typed.
%
It follows from the inferred resources used being the same for all bindings
that at most a single variable from the recursive group can be used in the
continuation.
%
The treatment of recursive let bindings in our system is discussed in Section~\ref{sec:recursivelets}.
